---
title: "R code for application of the Checklist for Health Economic Quality Evaluations (CHEQUE) in a systematic review setting"
author: "Stijntje Dijk"
date: "29-11-2023"
output: html_document
---

# Notes before running this code:
This repository was created to accompany the following manuscript "An application of the Checklist for Health Economic Quality Evaluations (CHEQUE) in a systematic review setting"

Stijntje W. Dijk MD MSc1,2, Skander Essafi MD3, Myriam G.M. Hunink MD PhD*1,2,4

1 Department of Epidemiology, Erasmus MC, University Medical Center Rotterdam, The Netherlands 2 Department of Radiology, Erasmus MC, University Medical Center Rotterdam, The Netherlands 3 Erasmus University Rotterdam, Rotterdam, The Netherlands 4 Center for Health Decision Science, Harvard T.H. Chan School of Public Health, Boston, USA

Correspondence: m.hunink@erasmusmc.nl

The manuscript was accepted for publication by Value in Health and will hopefully be shared online shortly. This repository contains all code that was written to create the traffic light plots and tables part of the paper. We used robvis package as inspiration for creating these plots based on the more common Risk Of Bias plots used in medical literature

All are invited to use and modify the provided code for their own project, though we appreciate a citation of our paper if you do.

This code loads and saves files under the assumption that it is opened within the context of the file folder. Please download the full R studio folder, or adjust the directories so that the appropriate files are loaded or saved in the correct location.
We have included the datafile for our study; Should the code be reused in a new context, please either use the same structure of our excel sheet, or adjust the column names in-code
To view the various sections of the code, use the "Outline" function in R studio to navigate through the code
We recognize that some sections of the code below can be written out in a more efficient manner. As this study is however not funded and coded in our free time, we prioritized that the code achieved its goals, and invite future users to optimize it further if they deem necessary


# Knitting setup
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "./") # set working directory to the root directory rather than another sub-folder where the RMarkdown file is saved
```

# Clean global environment
```{r, eval = FALSE}
# Clean list
rm(list = ls())
```

# Load required packages
```{r, eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
# If packages are not yet installed, do so first using the install.packages() function
library(ggplot2)
library(tidyverse)
library(readxl)
library(writexl)
library(dplyr)
library(gridExtra)
library(ggrepel)
library(cowplot)
```

# Load data
```{r}
# Select pathway to saved dataset containing the CHEQUE data
df_CHEQUE_full <- read_excel("../data/SR_Data.xlsx")

# Save full attribute names
full_names <- colnames(df_CHEQUE_full)

# Create copy and substitute full names for shortened attribute names
df_CHEQUE  <- df_CHEQUE_full
colnames(df_CHEQUE) <- sub("^([MR]\\d+).*", "\\1", colnames(df_CHEQUE_full))

# Remove the row for scoring weights as this contains no information
df_CHEQUE <- df_CHEQUE[!grepl("Scoring_weights", df_CHEQUE$Attribute), ]

# Remove the empty column that is between the two assessments
# Identify the column index between M24 and R1
col_index_to_remove <- which(colnames(df_CHEQUE) %in% c("M24", "R1"))[1]

# Remove the identified column
df_CHEQUE <- df_CHEQUE[, -(col_index_to_remove +1)]

# Print table
df_CHEQUE
```

# Setup color scheme
```{r}
# Choose the colors used in the code. The default colors chosen below are intended as colorblind friendly choices
color_full     <- "#009E73" # Assigned to "yes" scored items (full score is awarded)
color_somewhat <- "#F0E442" # Assigned to "somewhat" scored items
color_no       <- "#CC79A7" # Assigned to "no" scored items
color_na       <- "#D3D3D3" # Assigned to "N/A" scored itmes
```


# Select domains
```{r}
domain_vector_list <- unlist(df_CHEQUE[df_CHEQUE$Attribute == "Domain", -1])
domain_vector      <- unique(unlist(domain_vector_list))
domain_vector      <- domain_vector[!is.na(domain_vector)]
domain_vector
```

# Plot trafficlight per-study score 
The traffic-light and summary score-plots are made to resemble the Risk Of Bias tool plots, such as created through the "robvis" R package; https://www.riskofbias.info/welcome/robvis-visualization-tool
```{r}
# Function to create a custom traffic light plot for "Methods" or "Reporting"
custom_traffic_light_plot <- function(data, psize, overall) {

  # Split data into "Methods" and "Reporting"
  df_methods <- data %>% select(Attribute, starts_with("M")) %>% filter(!Attribute %in% c("Scoring_weight", "Rounded_importance_score", "Quality_assessment_section", "Domain"))
  df_reporting <- data %>% select(Attribute, starts_with("R")) %>% filter(!Attribute %in% c("Scoring_weight", "Rounded_importance_score", "Quality_assessment_section", "Domain"))

  # Melt the data frames for ggplot2
  df_melted_methods <- reshape2::melt(df_methods, id.vars = "Attribute", variable.name = "Study", value.name = "Score")
  df_melted_reporting <- reshape2::melt(df_reporting, id.vars = "Attribute", variable.name = "Study", value.name = "Score")

  # Define color scale based on the score
  color_scale <- scale_fill_manual(
    values = c("1" = color_full, "0.5" = color_somewhat, "0" = color_no, "N/A" = color_na),
    labels = c("1" = "yes", "0.5" = "somewhat", "0" = "no", "N/A" = "N/A")
  )

  # Sort attributes
  df_melted_methods$Attribute <- factor(df_melted_methods$Attribute, levels = unique(df_melted_methods$Attribute))
  df_melted_reporting$Attribute <- factor(df_melted_reporting$Attribute, levels = unique(df_melted_reporting$Attribute))

  # Order studies anti-alphabetically 
  df_melted_methods$Study <- factor(df_melted_methods$Study, levels = (sort(unique(df_melted_methods$Study))))
  df_melted_reporting$Study <- factor(df_melted_reporting$Study, levels = (sort(unique(df_melted_reporting$Study))))

  # Plot the figures side by side
  traffic_light_plot_methods <- ggplot(df_melted_methods, aes(x = Study, y = Attribute, fill = Score)) +
    geom_tile(color = "white", size = 1.5) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1),
          axis.text.y = element_text(angle = 0, hjust = 1),
          axis.title.x = element_blank(),  # Remove x-axis label
          axis.title.y = element_blank(),  # Remove y-axis label
          legend.position = "bottom",
          legend.title = element_blank(),
          legend.text = element_text(size = 10),
          panel.grid = element_blank()) +
    labs(title = "CHEQUE Quality assessment - Individual study scores",
         subtitle = "Methods",  # Update subtitle here
         fill = "Score") +
    color_scale

  traffic_light_plot_reporting <- ggplot(df_melted_reporting, aes(x = Study, y = Attribute, fill = Score)) +
    geom_tile(color = "white", size = 1.5) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1),
          axis.text.y = element_text(angle = 0, hjust = 1),
          axis.title.x = element_blank(),  # Remove x-axis label
          axis.title.y = element_blank(),  # Remove y-axis label
          legend.position = "bottom",
          legend.title = element_blank(),
          legend.text = element_text(size = 10),
          panel.grid = element_blank()) +
    labs(title = "",
         subtitle = "Reporting",  # Update subtitle here
         fill = "Score") +
    color_scale

  # Combine the two plots side by side
  combined_plot <- grid.arrange(traffic_light_plot_methods, traffic_light_plot_reporting, ncol = 2)

  # Save the plot to "../figures" folder
  ggsave(file.path("..", "figures", "traffic_light_plot.png"), combined_plot, width = 14, height = 6, units = "in")

  # Return the grid arrangement
  return(combined_plot)
}

# Run traffic light function "Methods" and "Reporting"
custom_traffic_light_plot(df_CHEQUE, psize = 12, overall = TRUE)
```


# Generate legend plot
```{r}
# Create a data frame for plotting
legend_data <- data.frame(full_names = full_names)

# Reverse the order of full_names
full_names_rev <- rev(full_names)

# Create a data frame for plotting
legend_data <- data.frame(full_names = full_names_rev)

# Create a data frame for names starting with 'R'
data_R <- data.frame(full_names = full_names_rev[grep("^R", full_names_rev)])
data_M <- data.frame(full_names = full_names_rev[grep("^M", full_names_rev)])

# Plot the legend with names starting with 'M'
legend_plot_M <- ggplot(data_M, aes(x = 0, y = seq_along(full_names), label = full_names)) +
  geom_text(size = 4, color = "black", hjust = 0) +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = margin(0, 0, 0, 0, "cm"),
        panel.spacing = unit(0, "lines"),
        plot.background = element_rect(fill = "white", color = "black"),
        text = element_text(color = "black", margin = margin(0, 0, 0, 0, "cm"), hjust = 0))

# Save the legend as an image file for names starting with 'M'
ggsave("../figures/legend_image_M.png", plot = legend_plot_M, width = 25, height = 6, dpi = 300)

# Plot the legend with names starting with 'R'
legend_plot_R <- ggplot(data_R, aes(x = 0, y = seq_along(full_names), label = full_names)) +
  geom_text(size = 4, color = "black", hjust = 0) +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = margin(0, 0, 0, 0, "cm"),
        panel.spacing = unit(0, "lines"),
        plot.background = element_rect(fill = "white", color = "black"),
        text = element_text(color = "black", margin = margin(0, 0, 0, 0, "cm"), hjust = 0))

# Save the legend as an image file for names starting with 'R'
ggsave("../figures/legend_image_R.png", plot = legend_plot_R, width = 25, height = 6, dpi = 300)
```

# Generate summary plot
## Get frequency of scores for each study 
```{r}
# Exclude unnecessary rows
count_df_study <- df_CHEQUE %>%
  filter(!Attribute %in% c("Quality_assessment_section", "Domain", "Rounded_importance_score"))

# Melt the data frame for counting
df_count_melted <- reshape2::melt(count_df_study, id.vars = "Attribute", variable.name = "Study", value.name = "Score")

# Count the frequency of each score for each attribute
count_df_study <- df_count_melted %>%
  group_by(Attribute, Score) %>%
  summarise(Frequency = n())

# Pivot the data frame for better visualization
count_df_study <- pivot_wider(count_df_study, names_from = Score, values_from = Frequency, values_fill = 0)
count_df_study
```

## Get frequency of scores for each attribute
```{r}
# Create df_count with only the relevant rows
df_count <- df_CHEQUE %>%
  filter(!Attribute %in% c("Quality_assessment_section", "Domain", "Rounded_importance_score"))

# Get all M and R column names
m_columns <- grep("^M\\d+$", names(df_count), value = TRUE)
r_columns <- grep("^R\\d+$", names(df_count), value = TRUE)

# Function to count and format data
count_and_format <- function(column_name) {
  count_result <- table(df_count[[column_name]])
  count_result <- as.data.frame(count_result)
  colnames(count_result) <- c("Score", column_name)
  return(count_result)
}

# Get all unique "Score" values
all_scores <- unique(unlist(lapply(c(m_columns, r_columns), function(column_name) df_count[[column_name]])))

# Apply the function to M columns
m_counts_list <- lapply(m_columns, count_and_format)
# Apply the function to R columns
r_counts_list <- lapply(r_columns, count_and_format)

# Function to merge with all_scores
merge_with_all_scores <- function(count_df) {
  result <- merge(data.frame(Score = all_scores), count_df, all.x = TRUE)
  result[is.na(result)] <- 0  # Replace NA with 0
  return(result)
}

# Apply the merging function to M counts
m_counts_list <- lapply(m_counts_list, merge_with_all_scores)
# Apply the merging function to R counts
r_counts_list <- lapply(r_counts_list, merge_with_all_scores)

# Combine the results into a single data frame
m_counts_df <- do.call(cbind, m_counts_list)
r_counts_df <- do.call(cbind, r_counts_list)

# Print the results
print(m_counts_df)
print(r_counts_df)

# Remove all columns named "Score" except the first one
m_counts_df <- m_counts_df[, !duplicated(colnames(m_counts_df))]
r_counts_df <- r_counts_df[, !duplicated(colnames(r_counts_df))]

m_counts_df
r_counts_df
```

## Generate summary chart
```{r}
# Function to create horizontal stacked percentage bar chart for all attributes
create_stacked_percentage_chart <- function(df_counts, attribute_prefix, title, subtitle) {
  attribute_order <- paste0(attribute_prefix, 24:1)
  
  df_counts %>%
    pivot_longer(cols = starts_with(attribute_prefix), names_to = "Attribute", values_to = "value") %>%
    group_by(Attribute, Score) %>%
    summarise(Count = sum(value)) %>%
    group_by(Attribute) %>%
    mutate(Percentage = Count / sum(Count) * 100) %>%
    mutate(Attribute = factor(Attribute, levels = attribute_order)) %>%
    ggplot(aes(x = Percentage, y = Attribute, fill = Score)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c(
      "0"   = color_no,
      "0.5" = color_somewhat,
      "1"   = color_full,
      "N/A" = color_na
    )) +
    labs(x = "Percentage", y = "Attribute", fill = "Score", title = title, subtitle = subtitle) +
    theme_minimal() +
    theme(legend.position = "bottom")
}

# Create horizontal stacked percentage bar chart for all M attributes with subtitle "Methods"
m_chart <- create_stacked_percentage_chart(m_counts_df, attribute_prefix = "M", title = "CHEQUE Quality Assessment - Summary", subtitle = "Methods")

# Create horizontal stacked percentage bar chart for all R attributes with subtitle "Reporting"
r_chart <- create_stacked_percentage_chart(r_counts_df, attribute_prefix = "R", title = "",subtitle = "Reporting")

# Combine plots for M and R attributes
combined_chart <- cowplot::plot_grid(m_chart, r_chart, ncol = 2)

# Save the combined chart to file
ggsave(file.path("..", "figures", "traffic_light_summary_plot.png"), combined_chart, width = 14, height = 6, units = "in", bg = "white")

# Print the combined plot
print(combined_chart)
```

# Calculate weighted scores for each study
```{r}
# Change Attribute to rowname
df_CHEQUE_weightedtotal <- df_CHEQUE %>% 
  column_to_rownames(var = "Attribute")

# Change to numeric
# Identify rows to keep as they are
rows_to_keep <- c("Quality_assessment_section", "Domain")

# Identify rows to convert to numeric
# Note, this method is chosen so that study names can be adjusted
rows_to_convert <- setdiff(rownames(df_CHEQUE_weightedtotal), rows_to_keep)

# Convert rows to numeric
df_CHEQUE_weightedtotal[rows_to_convert, ] <- lapply(df_CHEQUE_weightedtotal[rows_to_convert, ], as.numeric)

df_CHEQUE_weightedtotal
```

# Calculate weighted scores for Reporting, Methods and Total
```{r}
# Create subsets of df_CHEQUE to create three sets of score tables
## df_CHEQUE_M for only method items
selected_columns_M <- grep("^M", colnames(df_CHEQUE), value = TRUE)
df_CHEQUE_M <- df_CHEQUE %>%
  select(Attribute, all_of(selected_columns_M))
## df_CHEQUE_R for only reporting items
selected_columns_R <- grep("^R", colnames(df_CHEQUE), value = TRUE)
df_CHEQUE_R <- df_CHEQUE %>%
  select(Attribute, all_of(selected_columns_R))
## df_CHEQUE_T for full set
df_CHEQUE_T <- df_CHEQUE

calculate_scores <- function(df_CHEQUE_weightedtotal) {
 # Change Attribute to rowname
df_CHEQUE_weightedtotal <- df_CHEQUE_weightedtotal %>% 
  column_to_rownames(var = "Attribute")

# Change to numeric
# Identify rows to keep as they are
rows_to_keep <- c("Quality_assessment_section", "Domain")

# Identify rows to convert to numeric (studies)
rows_to_convert <- setdiff(rownames(df_CHEQUE_weightedtotal), rows_to_keep)

# Convert rows to numeric
df_CHEQUE_weightedtotal[rows_to_convert, ] <- apply(df_CHEQUE_weightedtotal[rows_to_convert, ], 2, as.numeric)

# Extract studies dynamically
studies <- rownames(df_CHEQUE_weightedtotal)[!(rownames(df_CHEQUE_weightedtotal) %in% c("Rounded_importance_score", rows_to_keep))]

# Extract items dynamically
items <- colnames(df_CHEQUE_weightedtotal)[!(colnames(df_CHEQUE_weightedtotal) %in% "Attribute")]

# Create dataframes for NA replaced with 1 and 0
df_CHEQUE_weightedtotal_NA1 <- df_CHEQUE_weightedtotal
df_CHEQUE_weightedtotal_NA0 <- df_CHEQUE_weightedtotal

# Create a dataframe to store calculated scores for each study
df_calculated_scores <- data.frame(Study = studies, Score_NA1 = numeric(length(studies)), Score_NA0 = numeric(length(studies)))

# Loop through studies and items to calculate weighted scores
for (study in studies) {
  # Replace NA with 1 in df_CHEQUE_weightedtotal_NA1
  df_CHEQUE_weightedtotal_NA1[study, items][is.na(df_CHEQUE_weightedtotal_NA1[study, items])] <- 1
  
  # Replace NA with 0 in df_CHEQUE_weightedtotal_NA0
  df_CHEQUE_weightedtotal_NA0[study, items][is.na(df_CHEQUE_weightedtotal_NA0[study, items])] <- 0
  
  df_CHEQUE_weightedtotal_NA1[study, items] <- as.numeric(df_CHEQUE_weightedtotal_NA1[study, items])
  
  # Extract the importance scores for the study
  importance_scores <- df_CHEQUE_weightedtotal["Rounded_importance_score", items]
  
  # Multiply each item score by its importance score
  weighted_scores_NA1 <- unlist(as.numeric(df_CHEQUE_weightedtotal_NA1[study, items])) * unlist(as.numeric(importance_scores))
  
  weighted_scores_NA0 <- unlist(as.numeric(df_CHEQUE_weightedtotal_NA0[study, items])) * unlist(as.numeric(importance_scores))
  
  # Save the calculated scores for each study
  df_calculated_scores[df_calculated_scores$Study == study, "Score_NA1"] <- sum(weighted_scores_NA1, na.rm = TRUE)
  df_calculated_scores[df_calculated_scores$Study == study, "Score_NA0"] <- sum(weighted_scores_NA0, na.rm = TRUE)
  
  # Create a third category for NA scores
  max_score <- sum(unlist(as.numeric(df_CHEQUE_weightedtotal["Rounded_importance_score", items])))
  max_score_NA <- max_score - (sum(weighted_scores_NA1, na.rm = TRUE)-(sum(weighted_scores_NA0, na.rm = TRUE)))
  
  # Save the max_score for each study
  df_calculated_scores[df_calculated_scores$Study == study, "Max_Score_ignore_NA"] <- max_score_NA
}

df_calculated_scores

# Add max score
max_score <- sum(unlist(as.numeric((df_CHEQUE_weightedtotal["Rounded_importance_score", items]))))
df_calculated_scores$Max <- max_score

# Round results by 2 decimals
# Round percentages to 2 decimals
df_calculated_scores$'% Max NA=1' <- round((df_calculated_scores$Score_NA1 / df_calculated_scores$Max) * 100, 2)
df_calculated_scores$'% Max NA=0' <- round((df_calculated_scores$Score_NA0 / df_calculated_scores$Max) * 100, 2)
df_calculated_scores$'% Max NA=ignore' <- round((df_calculated_scores$Score_NA0 / df_calculated_scores$Max_Score) * 100, 2)

  return(df_calculated_scores)
}

# Apply function
df_calculated_scores_M <- calculate_scores(df_CHEQUE_M)
df_calculated_scores_R <- calculate_scores(df_CHEQUE_R)
df_calculated_scores_T <- calculate_scores(df_CHEQUE_T)

df_calculated_scores_M 
df_calculated_scores_R
df_calculated_scores_T
```

# Rename and save weighted score tables
```{r}
rename_and_save_table <- function(df_calculated_scores_print, version) {
  # Rename columns
  df_calculated_scores_print_renamed <- df_calculated_scores_print %>%
    select(-`% Max NA=0`) %>%
    rename(
      "NA = 1" = Score_NA1,
      "NA = NA" = Score_NA0,
      "Max Score" = Max,
      "Max Score NA = NA" = Max_Score_ignore_NA,
      "% of Max Score" = `% Max NA=1`,
      "% of Max Score NA" = `% Max NA=ignore`
    )
  df_calculated_scores_print_renamed <- df_calculated_scores_print_renamed %>%
    select(Study, "NA = 1", "Max Score", "% of Max Score", "NA = NA", "Max Score NA = NA", "% of Max Score NA")
  
  # Save the table as a PNG image
  png_file_name <- paste0("../figures/df_calculated_scores_", version, ".png")
  png(png_file_name, width = 800, height = 600)
  grid.arrange(tableGrob(df_calculated_scores_print_renamed, rows = NULL), ncol = 1)
  dev.off()
  
  cat("Table saved as:", png_file_name, "\n")
  
  # Save the table as an Excel file
  excel_file_name <- paste0("../figures/df_calculated_scores_", version, ".xlsx")
  write_xlsx(df_calculated_scores_print_renamed, excel_file_name)
  
  cat("Excel file saved as:", excel_file_name, "\n")
}

# Rename and save the calculated scores
rename_and_save_table(df_calculated_scores_print=df_calculated_scores_M, "M")
rename_and_save_table(df_calculated_scores_print=df_calculated_scores_R, "R")
rename_and_save_table(df_calculated_scores_print=df_calculated_scores_T, "T")

```

# Create a correlation plot
```{r}
# Extract the relevant columns for the correlation plot
column_name_1 <- '% Max NA=1'
column_name_2 <- '% Max NA=ignore'
scores_M_1 <- df_calculated_scores_M[[column_name_1]]
scores_R_1 <- df_calculated_scores_R[[column_name_1]]
scores_M_2 <- df_calculated_scores_M[[column_name_2]]
scores_R_2 <- df_calculated_scores_R[[column_name_2]]
study_labels_1 <- df_calculated_scores_M$Study
study_labels_2 <- df_calculated_scores_R$Study

# Function to format p-values for the legend
format_p_value <- function(p_value) {
  if (p_value < 0.001) {
    return("<0.001")
  } else if (p_value < 0.01) {
    return("<0.01")
  } else {
    return(sprintf("%.3f", p_value))
  }
}

# Create a scatter plot with correlation coefficient and p-value inside the plot
plot_1 <- ggplot(data = data.frame(scores_M_1, scores_R_1, Study = study_labels_1), aes(x = scores_M_1, y = scores_R_1)) +
  geom_point(size = 1.1) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = color_full, fullrange = TRUE) +
  geom_label_repel(aes(label = Study), size = 3, box.padding = 0.5, max.overlaps = Inf, alpha = 0.8, 
                   fill = alpha("white", 0.7), color = "black", 
                   segment.color = "black", segment.linetype = "dotted", segment.alpha = 0.5) +
  labs(subtitle = "N/A = 1",
       x = "Absolute scores for Methods (M)",
       y = "Absolute scores for Reporting (R)",
       caption = sprintf("Correlation Coefficient: %.3f, p-value: %s", 
                         cor.test(scores_M_1, scores_R_1)$estimate, 
                         format_p_value(cor.test(scores_M_1, scores_R_1)$p.value))) +
  ylim(0, 100) + xlim(0, 100) 

plot_2 <- ggplot(data = data.frame(scores_M_2, scores_R_2, Study = study_labels_2), aes(x = scores_M_2, y = scores_R_2)) +
  geom_point(size = 1.1) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = color_no, fullrange = TRUE) +
  geom_label_repel(aes(label = Study), size = 3, box.padding = 0.5, max.overlaps = Inf, alpha = 0.8, 
                   fill = alpha("white", 0.7), color = "black", 
                   segment.color = "black", segment.linetype = "dotted", segment.alpha = 0.5) +
  labs(subtitle = "N/A = N/A",
       x = "% of max scores for Methods (M)",
       y = "% of max scores for Reporting (R)",
       caption = sprintf("Correlation Coefficient: %.3f, p-value: %s", 
                         cor.test(scores_M_2, scores_R_2)$estimate, 
                         format_p_value(cor.test(scores_M_2, scores_R_2)$p.value))) +
  ylim(0, 100) + xlim(0, 100) 

# Extract the relevant columns for correlation
column_name_1 <- 'Score_NA1'
column_name_2 <- 'Score_NA0'
scores_M_3 <- df_calculated_scores_M[[column_name_2]]  # Corrected column_name_1
scores_R_3 <- df_calculated_scores_R[[column_name_2]]  # Corrected column_name_1
study_labels_3 <- df_calculated_scores_M$Study         # Corrected study_labels_3

plot_3 <- ggplot(data = data.frame(scores_M_3, scores_R_3, Study = study_labels_3), aes(x = scores_M_3, y = scores_R_3)) +
  geom_point(size = 1.1) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = color_somewhat, fullrange = TRUE) +
  geom_label_repel(aes(label = Study), size = 3, box.padding = 0.5, max.overlaps = Inf, alpha = 0.8, 
                   fill = alpha("white", 0.7), color = "black", 
                   segment.color = "black", segment.linetype = "dotted", segment.alpha = 0.5) +
  labs(subtitle = "N/A = 1",
       x = "Absolute scores for Methods (M)",
       y = "Absolute scores for Reporting (R)",
       caption = sprintf("Correlation Coefficient: %.3f, p-value: %s", 
                         cor.test(scores_M_3, scores_R_3)$estimate, 
                         format_p_value(cor.test(scores_M_3, scores_R_3)$p.value))) +
  ylim(0, 100) + xlim(0, 100) 


# Combine the two plots using cowplot
overall_plot <- plot_grid(plot_1, plot_3, plot_2, labels = c("", ""), ncol = 3)

# Display the overall plot
print(overall_plot)

# Save the overall plot
ggsave("../figures/correlationplot_percentage_and_absolute_scores.png", overall_plot, width = 15, height = 5)
```



